Verifying Demonstrations

### 2021-06-17 paper/privacy-analysis.tex
Updates data in adversary model
Clarifies privacy analysis

However, there are more data than \(\pid, \wid\) used in the protocol.
The protocol uses \(\cid, \pid, \wid, t_s, t_s', l, \corr_\pid, \corr_\wid\).
The cause identifier \(\cid\) will be used for all proof shares
pertaining to the same protest and thus it cannot be used to uniquely
identify any individual. The location \(l\) is coarse enough so that many non-overlapping 
\((\pid, \wid)\)-pairs use the same location.
After all, it is the location of the protest, not the location within the 
protest that matters.
Thus \(l\) is not uniquely identifying any individual protester or witness.
Likewise, thanks to the constraints in the time-stamp granularity 
(\cref{timestamp}), \(t\) is not uniquely identifying either.

>>>>

However, there are more data than \(\pid, \wid\) used in the protocol.
The protocol uses \(\cid, \pid, \wid, t_s, t_s', l, \corr_{\pid}, 
\corr_{\wid}\).
The cause identifier \(\cid\) will be used for all proof shares
pertaining to the same protest and thus it cannot be used to uniquely
identify any individual. The location \(l\) must be coarse enough so that many 
non-overlapping \((\pid, \wid)\)-pairs use the same location.
After all, it is the location of the protest, not the location within the 
protest that matters.
Thus \(l\) can be made to not uniquely identify any individual protester or 
witness.
Likewise, thanks to the constraints in the time-stamp granularity 
(\cref{timestamp}), \(t\) can be made to not uniquely identify either.
